\renewcommand{\arraystretch}{1.4}

\begin{longtable}{|>{\raggedright\arraybackslash}p{2.4cm}|p{12cm}|}
\caption{Chapter Overview} \\
\hline
\multicolumn{2}{|c|}{\textbf{Chapter 2}} \\
\hline
\textbf{Topic} & \textit{Coastal geomorphological changes on southwestern Lake Michigan: Perspective from multi-scale} \\
\textbf{Question} & What are the coastal geomorphological changes on multi-scale in the coastline of southwestern Lake Michigan? \\
\textbf{Objective} & To characterize coastal geomorphological changes on different temporal and spatial scales. \\
\textbf{Contribution} & Provide an insight of bluff and shoreline change over both long-term and short-term periods, utilizing three distinct spatial scales. \\
\hline
\multicolumn{2}{|c|}{\textbf{Chapter 3}} \\
\hline
\textbf{Topic} & \textit{Wave climate on the southeastern Wisconsin coast of Lake Michigan: Perspective from wave directionality} \\
\textbf{Question} & Does wave directionality help identify the trend of wave climate? \\
\textbf{Objective} & To characterize the directional wave climate in the nearshore of southeastern Lake Michigan. \\
\textbf{Contribution} & Provide an approach to define the wave directionality and explore the implication of wave directionality. \\
\hline
\multicolumn{2}{|c|}{\textbf{Chapter 4}} \\
\hline
\textbf{Topic} & \textit{Wave climate on the southeastern Wisconsin coast of Lake Michigan: Perspective from wave systems} \\
\textbf{Question} & Does wave spectrum help identify the trend of wave climate? \\
\textbf{Objective} & To analyze the effect of swells and wind–sea waves at the nearshore of Lake Michigan. \\
\textbf{Contribution} & Illustrate the trend of wave climate by swell–wind–sea separation and by probability distribution in spectral occurrence map. \\
\hline
\multicolumn{2}{|c|}{\textbf{Chapter 5}} \\
\hline
\textbf{Topic} & \textit{Assessing coastal vulnerability using directional spectral wave climate: Coastal Vulnerability Index} \\
\textbf{Question} & How does the directional spectral wave climate impact the coastal vulnerability? \\
\textbf{Objective} & Develop an index to access the coastal vulnerability that is applicable to the directional spectral wave climate in Lake Michigan. \\
\textbf{Contribution} & Provide an insight in coastal vulnerability in Lake Michigan coastline. \\
\hline
\end{longtable}
